\Large \bf \sys: Library-Oriented Program Analysis

### 2020-05-26 paper/draft.tex
Add total, average numbers of downloads per week and dependencies

\heading{\sys on Popular Libraries}
For the first experiment, we perform a large-scale evaluation on 50 JavaScript packages from the npm ecosystem.
These libraries are highly popular, averaging \todo{xx-xx} weekly downloads (total: \todo{X}) and are depended upon by about \todo{XX} other packages or applications on average (total: \todo{X}).
These libraries are relatively small---adhering to known language trends~\cite{npmstudy:19}---simplifying compatibility inspection.

>>>>

\heading{\sys on Popular Libraries}
For the first experiment, we perform a large-scale evaluation on 50 JavaScript packages from the npm ecosystem.
These libraries are highly popular, averaging \todo{4842488} weekly downloads (total: \todo{227596957}) and are depended upon by about \todo{2} other packages or applications on average (total: \todo{75}).
% More results about the javascript packages here: https://docs.google.com/spreadsheets/d/18xKjCgj1phODbNi6_IT-y3vP3oVaaY5oA-Wux2avvGY/edit#gid=2071117281
These libraries are relatively small---adhering to known language trends~\cite{npmstudy:19}---simplifying compatibility inspection.
